Saint Helena Island Implementation

### 2025-01-13 Implementation doc/Draft1.Rmd
updating files

source("@_Region file.R")
Period <- "2010-2019"

@@

model <- StrathE2E2::e2e_read(implementation, Period, models.path="Files") # Load implementation

Area <- read.csv(str_glue("Files/{implementation}/{Period}/Param/event_timing_SAINT_HELENA.csv")) %>% 
  filter(str_detect(Description, "km2")) %>% 
  .$Value                                                     # Get size of the model domain

@@

physical <- read.csv(str_glue("Files/{implementation}/{Period}/Param/physical_parameters_ASCENSION.csv"))

>>>>

source("@_Region file.R")

@@

models <- StrathE2E2::e2e_ls("Files/")

model <- StrathE2E2::e2e_read("Saint_Helena_MA", "2010-2019-CNRM-ssp126", models.path = "Files")

Area <- read.csv(str_glue("Files/Saint_Helena_MA/2010-2019-CNRM-ssp126/Param/event_timing_SAINT_HELENA_MA_2010-2019-CNRM-ssp126.csv")) %>% 
  filter(str_detect(Description, "km2")) %>% 
  .$Value

@@

physical <- read.csv(str_glue("Files/Saint_Helena_MA/2010-2019-CNRM-ssp126/Param/physical_parameters_ASCENSION.csv"))
